Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
adopting sol's comment for SmallCheck.
skelton for shouldThrow.

@@

SmallCheck~\cite{smallcheck} is a tool for
automatic exhaustive testing at a certain level.
Both Doctest and Hspec do not have support for SmallCheck
at this moment.
\begin{itemize}
    \item
        \emph{sol: Hspec's mechanism for evidence is extensible.  It
        would be easy to add support for SmallCheck.}
\end{itemize}

@@

The {\tt testpack} package provides a function to check
exception, similar to {\tt shouldThrow}.

\begin{quote}
\small
\begin{verbatim}
assertRaises :: (Show a, Exception e, Show e, Eq e) =>
  String -> e -> IO a -> IO ()
\end{verbatim}\end{quote}

>>>>

\begin{quote}
\small
\begin{verbatim}
shouldThrow ::
  Exception e => IO a -> Selector e -> Assertion
\end{verbatim}
\end{quote}

@@

SmallCheck~\cite{smallcheck} is a tool for
automatic exhaustive testing at a certain level.
Both Doctest and Hspec do not have support for SmallCheck
at this moment.
Hspec's mechanism for evidence is extensible.
If necessary, it would be easy to support SmallCheck.

@@

The {\tt testpack} package provides a function to check
exception, similar to {\tt shouldThrow} described in Section~\ref{sec:hspec-comb}.

\begin{quote}
\small
\begin{verbatim}
assertRaises :: (Show a, Exception e, Show e, Eq e) =>
  String -> e -> IO a -> IO ()
\end{verbatim}
\end{quote}
